% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin



\newcommand{\person}{Recruiting Manager}
\newcommand{\position}{LabVIEW software test engineer }%TRAILING SPACE neeeded otherwise it butts up against the next word
\newcommand{\jobpostingsource}{Craigslist} %Monster.com
\newcommand{\phonenumber}{(507) 990-9052 }
\newcommand{\contactemail}{nick.klosterman@gmail.com}
%\newcommand

\begin{document}

\signature{Nick Klosterman}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 

 
\begin{letter}{ \person \\
Production Design Services, Inc. \\
401 Fame Drive \\
Dayton, OH 45449

}

  \begin{flushright}
 \hfill   \large\bf Nick Klosterman  \\
\end{flushright}
\begin{flushright}
    \medskip\hrule height 1pt
    \hfill 952 Westminster Place, Dayton, OH 45419 \\
    \hfill \phonenumber \\
    \hfill \contactemail
%\end{center}
  \end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear \person :} 

%PARAGRAPH ONE: State reason for letter, name the position or type of work you are applying for and identify source from  which  you learned   of   the  opening.  (i.e.  Career  Development  Center, newspaper, employment service, personal contact).  
\noindent 
I am interested in the \position position posted on \jobpostingsource.

%PARAGRAPH  TWO:  Indicate why you are interested in the position, the company, its products, services - above all, stress what  you can  do  for  the employer. If you are a recent graduate, explain how your academic background makes you a qualified candidate  for the  position.  If  you have practical work experience, point out specific achievements or unique qualifications. Try not to repeat the  same  information  the reader will find in the resume. Refer the reader to the enclosed resume or application which summarizes your  qualifications,  training,  and experiences. The purpose of this section is to strengthen your resume  by  providing  details which bring your experiences to life. 
\noindent
I have extensive experience in developing product test software as well as product development and testing. 
At IBM \& JDS Uniphase, I helped develop and modify LabVIEW code for product integration and production testing.
I also implemented data logging to MySQL and SQLite databases and automatic graph generation for easy data analysis to complement production testing.
I developed a Visual BASIC program that automated product report generation by querying these databases and graphing product performance data versus product specifications.
I also have experience developing C++ and Java applications as well as utilizing Matlab for data analysis.
While working for Siemens, I peformed quality engineering duties.
I performed failure analysis of returned products and identified the root cause. I worked with development engineers to identify and implement corrective actions on the production line.
I also performed ongoing quality control of product ramp up in anticipation of production line shut down.
 
\noindent 
%PARAGRAPH THREE: Request a personal interview and  indicate  your flexibility as to the time and place. Repeat your phone number in the letter and offer assistance to help in a speedy response. For example,  state that you will be in the city where the company is located on a certain date and would like to set up an  interview. Or,  state  that  you  will  call  on a certain date to set up an interview. End the letter by thanking  the  employer  for  taking time to consider your credentials. 
The \position sounds like a wonderful opportunity, and I would welcome the chance for an interview to discuss your needs and outline my strengths in person. 
You may reach me at \phonenumber or \contactemail.
Thank you for your time and consideration of my resume. I look forward to speaking with you.
 

\closing{Sincerely yours,} 
 

 
\encl{Resume}  				% Enclosures

\end{letter}
 

\end{document}






