% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Nick Klosterman}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{Recruiting Manger \\
Belcan  \\
11591 Goldcoast Drive\\
Cincinnati, OH
}

  \begin{flushright}
 \hfill   \large\bf Nick Klosterman  \\
\end{flushright}
\begin{flushright}
    \medskip\hrule height 1pt
    \hfill 952 Westminster Place, Dayton, OH 45419 \\
    \hfill (507) 990-9052 \\
    \hfill nick.klosterman@gmail.com
%\end{center}
  \end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear Recruiting Manager:} 

%PARAGRAPH ONE: State reason for letter, name the position or type of work you are applying for and identify source from  which  you learned   of   the  opening.  (i.e.  Career  Development  Center, newspaper, employment service, personal contact).  
\noindent 
I am interested in the software engineer position posted on Monster.com. 
Although I am comfortable and familiar with programming in Windows, my interest was piqued by your desire for a Linux candidate.
I am interested in pursuing software positions where I may also utililze and build my skills using the Linux operating system.

%PARAGRAPH  TWO:  Indicate why you are interested in the position, the company, its products, services - above all, stress what  you can  do  for  the employer. If you are a recent graduate, explain how your academic background makes you a qualified candidate  for the  position.  If  you have practical work experience, point out specific achievements or unique qualifications. Try not to repeat the  same  information  the reader will find in the resume. Refer the reader to the enclosed resume or application which summarizes your  qualifications,  training,  and experiences. The purpose of this section is to strengthen your resume  by  providing  details which bring your experiences to life. 
\noindent
My C++ programming experience includes console applications as well as GUI applications.
I have developed on both Windows and Linux platforms. 

\noindent 
I have 6+ years using various distributions of the Linux operating system. 
%In the past I have used Fedora and OpenSUSE. 
%Currently I am using Ubuntu and Arch.
I am familiar with several different window managers including Gnome, KDE, and IceWM.
I have written various scripts for the bash shell.  
Many of the scripts are small scripts that vary from automated downloading to data manipulation and entry into SQLite and MySQL databases. 
I have also written large complex scripts such as the Backcountry.com Deal of the Day Tracker, which may be seen in operation at http://www.djinnius.com/Deals,  which was written entirely in bash.

%writign test suite scripts/programs for testing
%dumping of data into a database (sqlite/mysql) for data analysis -->need to write that data analysis program!
%Python? GUI development and experience of layout and what things work or don't work

 
\noindent 
%PARAGRAPH THREE: Request a personal interview and  indicate  your flexibility as to the time and place. Repeat your phone number in the letter and offer assistance to help in a speedy response. For example,  state that you will be in the city where the company is located on a certain date and would like to set up an  interview. Or,  state  that  you  will  call  on a certain date to set up an interview. End the letter by thanking  the  employer  for  taking time to consider your credentials. 
The software engineering position sounds like a wonderful opportunity, and I would welcome the chance for an interview to discuss your needs and outline my strengths in person. 
You may reach me at (507) 990-9052 or nick.klosterman@gmail.com.
Thank you for your time and consideration of my resume. I look forward to speaking with you.
 

\closing{Sincerely yours,} 
 

 
\encl{Resume}  				% Enclosures

\end{letter}
 

\end{document}






