% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin



\newcommand{\contactperson}{Recruiter}
\newcommand{\contactCompany}{Club Z Tutoring}
\newcommand{\contactStreetAddress}{ }
\newcommand{\contactCityStateZip}{ }
\newcommand{\position}{tutor }%TRAILING SPACE neeeded otherwise it butts up against the next word
\newcommand{\jobpostingsource}{Craigslist} %Monster.com                                                                                                                                                           
\newcommand{\personalphonenumber}{(507) 990-9052}
\newcommand{\personalemail}{nick.klosterman@gmail.com}

%\newcommand

\begin{document}

\signature{Nick Klosterman}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 

 
\begin{letter}{\contactperson \\
\contactCompany \\
\contactStreetAddress \\
\contactCityStateZip 

}

  \begin{flushright}
 \hfill   \large\bf Nick Klosterman  \\
\end{flushright}
\begin{flushright}
    \medskip\hrule height 1pt
    \hfill 952 Westminster Place, Dayton, OH 45419 \\
    \hfill \personalphonenumber \\
    \hfill \personalemail
%\end{center}
  \end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear \contactperson :} 

%PARAGRAPH ONE: State reason for letter, name the position or type of work you are applying for and identify source from  which  you learned   of   the  opening.  (i.e.  Career  Development  Center, newspaper, employment service, personal contact).  
\noindent 
I am interested in the \position position posted on \jobpostingsource. 

%PARAGRAPH  TWO:  Indicate why you are interested in the position, the company, its products, services - above all, stress what  you can  do  for  the employer. If you are a recent graduate, explain how your academic background makes you a qualified candidate  for the  position.  If  you have practical work experience, point out specific achievements or unique qualifications. Try not to repeat the  same  information  the reader will find in the resume. Refer the reader to the enclosed resume or application which summarizes your  qualifications,  training,  and experiences. The purpose of this section is to strengthen your resume  by  providing  details which bring your experiences to life. 
\noindent
I am an electrical engineer graduate student currently seeking full time employment. I really enjoyed my previous tutoring experience and would love to do it part time as I seek full-time employment. If I found employment before the school year was out I would uphold my obligation and continue tutoring until the school year was out.

I have experience tutoring grade school and high school students. While working in Rochester, Minnesota I volunteered two times a week as a tutor at the Rochester Public Library. The tutoring was run completely by volunteers as a walk up service to anyone willing to show up. The main contingent of students were children of Somali refugees who were often struggling to overcome the language barrier and knowledge gap.
My tutoring strengths lie in math and science topics. I would be comfortable teaching math and physics up to advanced placement levels. I am less current with biology and chemistry based topics although I have tutored students these topics in the past.
When tutoring high school students I aimed to truly give the student an understanding of the subject at hand by working out and creating examples with the student. Grade school students I typically aimed to engage them in the topic by making the topic fun in some way so that they would stay on task as well as learn the material. 
\noindent 

%PARAGRAPH THREE: Request a personal interview and  indicate  your flexibility as to the time and place. Repeat your phone number in the letter and offer assistance to help in a speedy response. For example,  state that you will be in the city where the company is located on a certain date and would like to set up an  interview. Or,  state  that  you  will  call  on a certain date to set up an interview. End the letter by thanking  the  employer  for  taking time to consider your credentials. 
The \position sounds like a wonderful opportunity, and I would welcome the chance for an interview to discuss your needs and outline my strengths in person. 
You may reach me at \personalphonenumber or \personalemail.
Thank you for your time and consideration of my resume. I look forward to speaking with you.
 

\closing{Sincerely yours,} 
 

 
\encl{Resume}  				% Enclosures

\end{letter}
 

\end{document}






