\begin{category}{Projects}
%\citembullet {Stock visualization project}
%data loggin of workouts
%ibd teext extractor
%arduino project
%\citembullet {Password SQLite Dbase} use one-time-pad algorithm
% \citembullet Data logging of workouts

%\citem { Desktop Stock Tracker 2012 }
%\begin{itemize}
%\item
%\end{itemize}

\citem {Revved Node.js Class : Modulus.io Status API }
\begin{itemize}
\item Class taught by MyRepp.com and Modulus.io founders.
\item Learned basics of using Node.js and middleware packages such as Express and Connect
\item Learned basics of templating using Handlebars.
\item Class project involved developing an API to report status of various Modulus.io systems.
\end{itemize}

\ifWebLinks
\citem { All project source code viewable on \href{ https://github.com/nickklosterman?tab=repositories }{ https://github.com/nickklosterman} }
\else
\citem { All project source code viewable on https://github.com/nickklosterman} 
\fi

\citem { Stock App November 2013 }
\begin{itemize}
\item Node.js app for viewing stock data from onlin top 50 lists
\item Data stored in SQLite and displayed using jQuery Sparklines (http://omnipotent.net/jquery.sparkline/)
\end{itemize}


\citem { Ohio Real Estate Google Maps Mashups 2012-2014 }
\begin{itemize}
\item Wrote software to parse foreclosure, real estate sales, and rental registration data from county websites and enter into private MySQL database.
\item Geocoded data and plotted data using google maps api.
\item Developed front end to query database for properties of interest.
\item Continually developing new parsers and adding data to database for new counties of interest.
\item Data updated weekly.

\ifDjinniusLinks
\ifWebLinks
\item Viewable at \href{ http://www.djinnius.com/SheriffSales/ }{ http://www.djinnius.com/SheriffSales/}
\else
\item Viewable at  http://www.djinnius.com/SheriffSales/
\fi
\fi

\end{itemize}

\citem { Desktop Stock Tracker 2012-2013 }
\begin{itemize}
\item Developed stock tracking software in Python to track performance of brokerage account.
\item Program calculates various metrics including annualized gain and capital gains taxes upon sale.
\item Program interfaces with Yahoo! Finance to obtain financial information.
\end{itemize}



\citem { Backcountry.com Deal of the Day Tracker 2011-2013 }
\begin{itemize}
\item Wrote software to track deals of the day appearing on Backcountry.com's outdoor \& sports deal websites and notify users when items of interest are featured.
\item Alerts based off of keyword matching are sent via text message or email.
\item Details of featured deals logged to a MySQL database. 
\item Developed online front-end to allow for users to add their own notifications as well as to view past product details from the product database.
\ifDjinniusLinks
\ifWebLinks
\item Viewable online at \href{ http://www.djinnius.com/Deals/ }{http://www.djinnius.com/Deals}.
\else
\item Viewable online at http://www.djinnius.com/Deals.
\fi
\fi
\end{itemize}

\citem { Bejeweled Bot June-July 2012 }
\begin{itemize}
\item Wrote C++ program to play Bejeweled.
\item Program grabs game window and parses game board.
\item Wrote logic to find legal moves on game board and to perform optimal move.
%\item Optimal move found by recursively simulating moves on current board determining which legal move has the most subsequent moves on resultant board.
\end{itemize}


%\citem {Comic Converter for Kindle and Android 2012 }
%\begin{itemize}
%\item Program optimizes comic archives for viewing on Kindle's grayscale screen and for color Android devices.
%\item Program utilizes Imagemagick libraries and can perform any Imagemagick function to optimize or refine images.
%\item Program can be run recursively optimizing any comic archives found. Can delete original archive upon completion to minimize disk usage.
%\end{itemize}

%\citem {Investor's Business Daily 100 Stock List Financial Visualization 2011}
%\begin{itemize}
%\item Project analyzes advertised returns of Investor Business Daily 100 stock list versus what return a typical investor might experience.
%\item Stock movements and rankings visualized to show movement of stocks onto and off of stock list.
%\item Leveraged Prefuse visualization package for rapid construction of data visualization.
%\end{itemize}

\end{category}
