\begin{category}{Work \\experience}
\citem{Freelance Software Engineer}, Present
\begin{itemize}
\item Revved Class project : Modulus status project for Modulus.io 
\item How/where do I stick in this class
\item Learned various aspects of developing an API and application on top of Node
\item Topics covered included routes, authentication, middleware, writing test suites, templating
\item Developed an application as part of the class project: Mongo, Mongoose, Handlebars
\end{itemize}

\citem{Software Engineer}, \href{http://www.intelligrated.com}{Intelligrated Systems LLC} August 2012 - Present
\begin{itemize}
%\item Contract to FT Hire via Aerotek, FT April 29th is official start)
\item Team member implementing next generation of warehouse conveyor control software suite to browser based application.
\item Wrote panels for web-based platform to match style and functionality of Windows .NET based panels. %hmm what is a panel? is it evident what that entails and what skills I have from that statement?
\item Developed Front End design (CSS, HTML5) and Back End logic adhering to MVVM pattern with Kendo UI. %Should I split this into two separate bullets? or keep it succinct and not add items that could be perceived as fluff. short and sweet.
\item Documentation of Remoting : interpreted princiapl engineer's demonstration code and created tutorial with demonstration code for our Quick Start Guide %flesh this out as it was more a tutorial to get a person up and running, quick start guide.
\item Wrote Group Folder Module : Module provides slide out menu of available panels to load into main window. Framework component

%\item Leveraged MVVM, Kendo data-binding \& widget usage, jQuery, kendo and jqueyr are proly both good things to mention

%\item -\> state use of proprietary framework utilizing Kendo as a base and working with modified widgets
%\item -\> context menu addition for grid ex. I didn't write the plugin so I don't know how much credit I can take. Jeff did more than I did. maybe state evaluated use of plugin?
\item Developed Line Sorter Panel using our internally developed custom framework to acquire and display data from databases and real time hardware sensors.

\item Initiated training sessions for new members to javascript team. helped guide n00bz through the gotchas of our framework and the peculiarities to the javascript language
%as Adam Eewing stated, we like to do things the hard way. instead of training people on the template and our custom framework , we like to make people stumble their way through it. 
%reasons to leave: they made it harder than it needed to be, they were awful at training their employees on the internal tools they made. ; but basically, I left bc I didn't liek it. I'm now focused on finding a place where I DO like it and I can learn a lot
%state that they made it harder on themselves and wouldn't listen to common sense. wouldn't listen to me when tried to initiate training program. 
%''Are we learnign from our mistakes?'' is answered with a 'no' here.
%\item visual studio templates
\item Configured open source jsdoc-toolkit to produce documentation from source code.
\item Modified C\# source code preprocessor to work with jsdoc-toolkit. %this is laughable. its not really an accomplishment as much as a sign that the place I worked at is fucked up. 
\item Created demonstration panel of available widgets to show capabilities to internal Intelligrated customers. 
%\item Customers were internal teams, provided customer support
\item Responsible for weekly merges of code branch with Trunk.
\item Wrote script to automate majority of merge steps to ensure process is followed, free up resources, and produce repeatable results. %Wrote Cygwin bash script automating repetitive steps of merge process including test builds and  Goddamn it!! this sounds stupid bc this shit should be automatically tested and not manually tested. How can I get this sthit to be automatically done instead of manually done?

%-->boost up your personal projects and show some progress in Github so you can still tout those. Orstate that you're racing and training a bunch. 
%Nah people don't care so much about that. They hire you for your skills and are less concerned with your hobbies.
%But show what you've learned and how you've improved the old apps using the new JS etc knowledge.


\end{itemize}


% Should I put some of the focus on classes that I took 

% 15-05-2012 I believe at this point that it is just as important what I'm doing now as it is what I've done in the past
\citem{Research  Assistant}, \href{http://www.purdue.edu}{Purdue University}  August 2007 - July 2010 
\begin{itemize}
%PRIME
\item Updated weather visualization software with requested features from Purdue University's Earth \& Atmospheric Sciences faculty.
\item Implemented data color coding to allow for easier analysis of convection paths in simulation datasets.
\item Implemented pop-up of 2D image slice of selected convection path. %this seems a bit lame...too specific?
%education module
\item Co-developed education module that discussed pros, cons, and pitfalls associated with various software visualization techniques.
\item Presented education module to Indiana Teachers as part of a workshop emphasizing computer visualization in the classroom.
\item Presented Google Maps visualization exercise to Indiana High School students. The exercise demonstrated the geographic effect of a terrorist act in an urban and rural setting as part of a Homeland Security class.
%Muscatatuck
%\item  what did I really do on this one?
\end{itemize}

\citem{Quality Engineer}, \href{http://www.energy.siemens.com/entry/energy/hq/en/}{Siemens Energy and Automation}, Bellefontaine, OH  2007 
\begin{itemize}
\item Analyzed customer's returned materials establishing root cause of failure.
\item Evaluated failures, identified solution, and implemented corrective action on manufacturing line.
\item Wrote technical documents reporting root cause failure of product to customer.
\item Conducted ongoing product reliability testing.
\item Implemented real time reliability plan to support product build up prior to plant shutdown.
\item Improved Visual Basic code for MS Access database to streamline data logging of samples and to make report generation easier.
\end{itemize}
%interacted with cliff for root cause

\citem{Qualification and Integration Engineer}, \href{http://www.ibm.com}{IBM} \& \href{http://www.jdsu.com}{JDS Uniphase}, Rochester, MN  2001 - 2006 
\begin{itemize}
\item Performed optical to electrical and electrical to optical characterization tests on 1 Gb/s, 2 Gb/s, and 4 Gb/s fiber optic transceivers to prove compliance with Fibre Channel and Gigabit Ethernet standards. Tests included: Fiber coupled power, optical deterministic jitter, stressed receiver sensitivity, and mask margin.
\item Modified LabVIEW code to accommodate new products and additional tests.
\item Co-developed software to allow customer to interface with transceiver's onboard microprocessor. Provided live graph functionality as well as status notification of key onboard characteristics.
\item Led review of product qualification report with lead engineers and product manager.
\item Wrote software to automate qualification report generation from MS Access database.
%need to be knowledegeable enough for when they ask you about what you did that it doesn't look like your making shit up.
%was asked to stick around past previous termination date
%placed documents in that stupid online RCS system
%focal interface for reports when marketing wanted them.
\end{itemize}

%played rugby, coached rugby, got PPLicense, volunteer tutor, took comm ed classes
%HKN at purdue, cycling lead at purdue

\citem{Volunteer Research Assistant}, Mayo Clinic, Rochester, MN  2005 
\begin{itemize}
\item Developed software module for in house ANALYZE software suite allowing for analysis of Computed Tomography images. 
\item Module performed kidney stone detection and sizing to determine health risk score for patient.
\item Volunteered time to learn more about commercial applications of image analysis. 
%\item scans of kidney stones in CT assessed for health risk to patient
%\item What action words? What skills learned from this exp? Tcl.
\end{itemize}


%\citem{Wright-Patterson Air Force Base \\ Air Force Research Lab \\ Air Vehicles Directorate}, Dayton OH ( 2000 )
\citem{Wright-Patterson Air Force Base}, Dayton OH  2000 
\begin{itemize}
\item Developed Java applet simulating unmanned autonomous vehicles.
%\item Implemented flocking algorithm to control agents 
\item Implemented flocking algorithm to control vehicle interaction.
\end{itemize}

%\citem
%\begin{itemize}
%\item
%\end{itemize}


\end{category}
